formula1

### 2020-05-25 inst/skating_analysis.Rmd
cache expensive results
keep just the top competitors, alternative to zapweak()

```{r,maxshow}
(m <- maxp(skating))
```

@@

```{r,unconstrainedlikes}
mgv <- maxp(skating, give=TRUE, n=2)$value
mgv  - out
mgv  - max(out)
```

@@

>>>>

```{r,maxshow, cache = TRUE}
(m <- maxp(skating))
```

@@

```{r,unconstrainedlikes, cache=TRUE}
mgv <- maxp(skating, give=TRUE, n=10)$value
mgv  - out
mgv  - max(out)
```

@@

# Just the top seven competitors

```{r}
skating_table
o <- ordertable_to_ranktable(skating_table)
o
class(o) <- "matrix"
o
o <- o[,1:7]
o
o <- t(apply(o,1,rank))
colnames(o) <- rownames(skating_table)[1:7]
o
class(o) <- "ranktable"
o
o <- ranktable_to_ordertable(o)
o
o <- ordertable2supp(o)
o
o <- maxp(o)
pie(o)
```
